TacticToe: Learning to Prove with Tactics

### 2018-03-14 tactictoe_jv.tex
ack

\paragraph{Acknowledgments}\label{sect:acks}
We would like to thank Lasse Blaauwbroek and Yutaka Nagashima for their 
insightful comments which
contributed to improve the quality of this paper. This work has been supported
by the ERC Consolidator grant no.\ 649043 \textit{AI4REASON} and ERC starting
grant no.\ 714034 \textit{SMART}.

>>>>

\paragraph{Acknowledgments}\label{sect:acks}
We would like to thank Lasse Blaauwbroek and Yutaka Nagashima for their 
insightful comments which
contributed to improve the quality of this paper. This work has been supported
by the ERC Consolidator grant no.\ 649043 \textit{AI4REASON}, the ERC starting
grant no.\ 714034 \textit{SMART}, the Czech 
project AI \& Reasoning CZ.02.1.01/0.0/0.0/15\_003/0000466 and the 
European Regional Development Fund.
